### 2013-09-19 intro.tex
Polish intro, add blank chapter on evaluation

Before we delve into semantic segmentation and object class recognition, we
will first investigate general grouping mechanisms in Chapter~\ref{ch:itm}.
Clustering is an important step in most semantic segmentation pipelines, in at
least two places: bottom-up segmentation and creation of dictionaries for
feature learning. Chapter~\ref{ch:itm} introduces a novel, information theoretic
algorithm that compares favourably with algorithms from the literature.
While we do not apply our algorithm to the task of bottom-up segmentation,
this is a promising avenue for future research.

@@

\section{List of Contributions}
This thesis contains the following contributions:
\begin{itemize}
\item Introduction of general clustering algorithm that improves upon widely used
    approaches from the literature.
\item Demonstration of an algorithm for  weakly supervised object class segmentation.
\item Providing a general efficient implementation for structured prediction.
\item Analysis of max-margin learning algorithms with exact or approximate inference in different applications.
\item Demonstrating that exact learning for semantic segmentation and object class segmentation is possible in loopy graphs.
%\item Shows importance of edge features.
\end{itemize}

\section{Thesis Outline}
We start by introducing a novel clustering algorithm in Chapter~\ref{ch:itm},
which we plan to use as an additional building block for semantic segmentation
algorithms in future work. Clustering is important both for the initial
segmentation into superpixels, and in the creation of visual words.

We will then introducing a mostly unstructured
approach to semi-supervised learning for object class segmentation in
Chapter~\ref{ch:semi_supervised}, investigating the problem of annotating
training data for semantic segmentation. The central topic of this thesis is
introduced in Chapter~\ref{ch:structured_pystruct}, which also introduces our
software library for implementing structured learning and prediction
algorithms.
Chapter~\ref{ch:comparision} gives a quantitative comparison of the most widely
used structured prediction algorithms, focusing on which algorithm is best to
use in a given situation. In particular, we investigate learning behavior for
semantic segmentation on several datasets.

@@

Finally, Chapter~\ref{ch:nyu} applies the methods developed in
Chapter~\ref{ch:structured_pystruct} and Chapter~\ref{ch:exact_learning} to the
problem of semantic annotation with structure classes in RGB-D data. We
demonstrate that we are able to learn meaningful spacial relations, and improve
upon the state-of-the-art in the NYU V2 datasets that we consider.

>>>>

@@

\section{List of Contributions}
This thesis contains the following contributions:
\begin{itemize}
\item Introducing a general clustering algorithm that improves upon widely used
    approaches from the literature.
\item Demonstrating a scalable algorithm for weakly supervised object class segmentation.
\item Providing a general and efficient software framework for structured prediction.
\item Analysing  max-margin learning algorithms with exact or approximate inference in different applications.
\item Showing that exact learning for semantic segmentation and object class
    segmentation is possible in practice, even in loopy graphs.
\end{itemize}

\section{Thesis Outline}
Before we delve into semantic segmentation and object class recognition, we
will first investigate general clustering algorithm in Chapter~\ref{ch:itm}.
Clustering is an important step in most semantic segmentation pipelines, in at
least two places: bottom-up segmentation and creation of dictionaries for
feature learning. We introduce a novel, information theoretic algorithm that
compares favourably with algorithms from the literature.  While we do not apply
our algorithm to the task of bottom-up segmentation, this is a promising avenue
for future research.

We will then introducing a mostly unstructured
approach to semi-supervised learning for object class segmentation in
Chapter~\ref{ch:semi_supervised}, investigating the problem of annotating
training data for semantic segmentation.

The central topic of this thesis is introduced in
Chapter~\ref{ch:structured_pystruct}, which also introduces our software
library for implementing structured learning and prediction algorithms.

Chapter~\ref{ch:comparison} gives a quantitative comparison of the most widely
used structured prediction algorithms, focusing on which algorithm is best to
use in a given situation. In particular, we investigate learning behavior for
semantic segmentation on several datasets.

@@

Finally, Chapter~\ref{ch:nyu} applies the methods developed in
Chapter~\ref{ch:structured_pystruct} and Chapter~\ref{ch:exact_learning} to the
problem of semantic annotation with structure classes in RGB-D data. We
demonstrate that we are able to learn meaningful spacial relations, and improve
upon the state-of-the-art on the NYU V2 datasets.
